%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{fontspec}
\usepackage{tabularx}
\usepackage{ragged2e}
% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\usepackage{multicol}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Aleksei}{Sholokhov}
% \title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{202 Lewis Hall, Seattle, WA 98105}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
% \phone[mobile]{909-839-3097}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
% \email{xpan1@swarthmore.edu}                               % optional, remove / comment the line if not wanted
% \homepage{shawnpan.me}                         % optional, remove / comment the line if not wanted
% \extrainfo{}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c c }
 \faGlobe\enspace aksholokhov.github.io & \faEnvelopeO\enspace aksh@uw.edu & \faGithub\enspace aksholokhov & \faMobile\enspace 505-557-59-81\\  
\end{tabular}
\end{center}

\section{EDUCATION}
{\customcventry{Expected Graduation: 07/2023}{Ph.D. in Applied Mathematics}{University of Washington}{Seattle, WA}{}{}}
{\customcventry{07/2021}{M.Sc. in Applied Mathematics}{University of Washington}{Seattle, WA}{}{}}

\section{SKILLS}

\customcventry{09/2018-now}{As Research Assistant at the Institute for Health Metrics and Evaluation (IHME)}{Data Science and Data Analytics}{Seattle, WA}{}
{\begin{itemize}
	\item Devised new statistical modeling tools to improve the reliability of machine learning models in population health applications. Implemented it as a \texttt{python} package \texttt{skmixed}; achieved 30-fold speed-up upon deployment to the company's pipelines.
	\item Developed IHME Projections: a statistical model that projects cases and deaths from COVID-19 globally; in collaboration with a team of 130 researchers. This tool helped the decision makers (including national, state, and local governments) to allocate resources and plan ahead during the pandemic.
\end{itemize}
}

\customcventry{09/2018-now}{As Research Assistant at University of Washington}{Research in Machine Learning Algorithms and Deep Learning}{Seattle, WA}{}
{\begin{itemize}
	\item Created an algorithm to extract interpretable models and learned physics laws from trained neural networks. Decreased the amount of data needed to model noisy dynamical systems by 90\%.
	\item Accelerated deep neural network training using  Fletcher-Reeves and Newton-Krylov methods, and implemented image recognition libraries using \texttt{TensorFlow} and \texttt{jax} that achieved state-of-the-art performance for selected image recognition tasks.
\end{itemize}
}


\customcventry{09/2018-now}{As Research Assistant at University of Washington and IHME}{Software Development in Python, Scala, and C++}{Seattle, WA}{}
{\begin{itemize}
    \item Developed \texttt{gspack}: python-autograder to accelerate grading of coding assignments. This package is successfully used for 5 scientific computing classes for over 3000 students in Department of Applied Mathematics.
 	\item Enabled SVM classifiers to work with large-scale data using stochastic optimization. Implemented it as an open-source package \texttt{MEMOIR} using SQL, C++, and Python. Improved the accuracy and memory management by 30\% over state-of-the art approaches.
\end{itemize}
}

\customcventry{02/2016-07/2018}{As Research Student at Computing Center of Russian Academy of Science}{Project Management, Communication, Teamwork}{Moscow, Russia}{}
{\begin{itemize}
    \item Developed strong analytical, communication, and quantitative problem-solving skills by teaching graduate-level classes on Scientific Computing, HPC, and Optimization to classes of 200+ students (UW).
    \item Lead \texttt{rysearch} project: an exploratory data analysis and recommender system that simplifies knowledge discovery with NLP techniques such as topic-modeling. Implemented using \texttt{python}, \texttt{JavaScript}, and \texttt{MongoDB}.
    \item Effectively organized research and software development in the team of 4 researchers and successfully met tight deadlines. Published 2 novel quality metrics for topic models based on this work.
   	\end{itemize}
} 


\section{SELECTED PUBLICATIONS}
\vspace{0.3em}   	
 
 \begin{itemize}
 		\item \textbf{``Universal Feature Selection for Mixed-Effects Models with Non-convex Penalties"} \newline Together with Santomauro D., Burke J., Zheng P., and Aravkin A., \emph{in preparation}
 		\item \textbf{``Distillation of Neural Differential Equations for Interpretable Model Discovery"} \newline
 			 Together with Kutz, N., and Brunton, S. \emph{in preparation}
 		\item \textbf{``pysr3: Python Library for Sparse Relaxed Regularized Regression"} \newline
 			 Together with Zheng, P., and Aravkin, A., \emph{under peer-review}
        \item \textbf{``Modeling COVID-19 scenarios for the United States''}. \newline Together with IHME Covid-19 Forecasting Team. \emph{Nature Medicine}, 2020.
        \item \textbf{``Quality Evaluation and Improvement for Hierarchical Topic Modelling.''},\newline Together with Belyy A.V., Selezniova, M.S., and Vorontsov, K., \newline \emph{ 24rd International Conference on Computational Linguistics and Intellectual Technologies} 
        \item  \textbf{``MEMOIR: Multi-class Extreme Classification with Inexact Margin."} \newline Together with Belyy,~A.,\textit{arXiv preprint arXiv:1811.09863 (2018)}.
    \end{itemize}


\section{SERVICE AND OUTREACH}
\customcventry{09/2020 - Now}{Diversity, Equity, and Inclusion (DEI) Committee Member}{Department of Applied Mathematics, University of Washington}{Seattle, WA}{}
{\begin{itemize}
	\item Developed 10-years Diversity Action Plan for the Department of Applied Mathematics
	\item Organized and led educational seminars on importance of diversity in academia.
	\item Interviewed faculty job candidates to assess their DEI action track.
\end{itemize}
}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
