\section{Job Application Letter}

Dear NREL's Team,

After examining your job posting I am enthusiastically applying for the Researcher position in Machine Learning for Optimization for Energy Systems at NREL because I believe that I am an excellent candidate.

I have successfully completed projects in machine learning for modeling physical systems that perfectly align with your job posting. As an intern at Los Alamos National Laboratory (LANL), I applied reinforcement learning algorithms for controlling ensembles of hearing systems and air conditioners, which resulted in my undergraduate thesis. Then, as a PhD student in applied mathematics at the University of Washington, I developed novel optimization methods for statistical learning applications in population health settings. As a result, I published three papers and developed an open-source package that is now widely used at the Institute for Health Metrics and Evaluations (IHME) and beyond. Finally, for the last year I have been working with Mitsubishi Electric Research Laboratories (MERL) on physics-informed machine learning for reduced-order modeling of gas and fluid systems. During my internship, I drove a project from conception to publication in under three months and contributed significantly to an additional paper. In autumn 2022, I was hired as a consultant by MERL to provide guidance on machine learning and differentiable programming applications for an array of their projects. I believe that these experiences make me a perfect candidate for the job of Machine Learning Researcher at NREL. 

I am writing with keen interest in NREL's core values in environmental justice and creating sustainable ways of life, because they mirror my own. I am looking forward to applying my skills to secure a sustainable future for the planet while collaborating in a diverse, interdisciplinary, and multi-cultural team of like-minded scientists. Letters of recommendation from each institution mentioned above are openly available on my LinkedIn profile, and examples of my coding projects are available on my GitHub page; I attach both links to my job application. Please don't hesitate to contact me or any of my recommenders if you have any questions. 

I am greatly looking forward to hearing from you and hope that you have a wonderful day.